GEE models

### 2017-07-01 doc/manuscript.Rmd
moved plsda/lcmm results to vig

## Latent trajectories and differences in NEFA composition

Three latent classes were extracted from LCMM, with `r lcmm.groups$Freq[2]` 
participants in the high, `r lcmm.groups$Freq[1]` in the middle, and 
`r lcmm.groups$Freq[3]`
in the low beta-cell function groups. The trajectories of these groups are
shown in `r cite_sf('lcmm')`. These groups were used as the beta-cell function
response variables in the PLS-DA analysis, which was used to confirm the results
of the GEE modeling, but in a multivariate environment (all NEFA in a single
model). The PLS-DA results show a very poor discriminatory ability of the
NEFA composition in classifying participants into the correct beta-cell function
latent class. The percent of participants correctly predicted to belonging to
their group (i.e. those predicted in the low group and actually belonging to the
low group) was `r misclass.n.percent.bcf$Percent[9]` in the low group,
`r misclass.n.percent.bcf$Percent[5]` in the middle group, and 
`r misclass.n.percent.bcf$Percent[1]` in the high group (the distribution of the
groupings based on the components from PLS-DA are shown in `r cite_sf('plsda_groups')`). 
The loadings plot of the NEFA composition against the extracted PLS-DA
components is shown in `r cite_sf('plsda_loadings')` and is used to identify
fatty acids that contribute the most explained variance to the beta-cell
function groupings. However, because of the high rate of misclassification, no
meaningful predictive information can be extracted even if any NEFA does
contribute to the explained variance (e.g. 16:0). The PLS-DA analysis using
conversion to or maintenance of dysglycemia status over the 6 years as the
response variable showed similar poor discriminatory ability, though better than
the beta-cell function trajectory results. While 
`r misclass.n.percent.dysgly$Percent[1]`
of participants were correctly predicted to not have dysglycemia, only 
`r misclass.n.percent.dysgly$Percent[4]` were correctly predicted to have
dysglycemia (see `r cite_sf('plsda_groups_dysgly')` for the distribution of 
dysglycemia status based on the components from the PLS-DA and 
`r cite_sf('plsda_loadings_dysgly')` for the loadings plot of the NEFA composition
by extracted PLS-DA components). The results from the PLS-DA analysis are consistent
with the associations seen in the GEE models.

>>>>

```{r figure2, dependson='geeData', fig.cap=fig_gee}
gee_results %>% 
    dplyr::filter(model == "Adjusted") %>% 
    plot_gee_main()
```
